Using Scipion for Stream Image Processing at EM Facilities

### 2018-03-19 2.overall.tex

\section{Main Modifications introduced in  \scipion: Streaming, Monitors and Consensus}
\label{overall}
[**ROB this section goes not flow smoothly, needs a second pass]

@@

\scipion stream implementation is based on periodic updates of the protocol input and output data during the image processing. 
[**JMRT The following description is not accurate...Since \scipion runs on threads, it is possible to devote one thread to update these information while the rest of the CPU power is devoted to run the different protocols. The use of threads marks an important difference between running a script or using \scipion, since  each module is run independently creating a very flexible processing framework][**ROB: Any suggestion to make it more accurate?]. \scipion allows users to modify the workflow on the fly without modifying a single code line. The modification will not interfere with the already executed steps and may take advantage from all already computed data. By default \scipion will automatically stop after 24 hours with no microscope activity, but you may  continue the acquisition after a stop by pressing the continue button, there is no need to restart from the beginning.

@@

Since \scipion original publication we have developed many \emph{metaprotocols} [**JMRT not sure if the 
introduction of the metaprotocols definition helps the reader...anyway, there are metaprotocols in the first
version, so this is not completely new][**ROB there is no claim that the concept of metaprotocol is new, The only claim is that many protocols of this kind have been introduced in this version], that is, 
protocols that either check the progress of other protocols or compare the results of equivalent protocols.

>>>>

\section{Main Modifications introduced in  \scipion: Streaming, Monitors and Consensus}
\label{overall}
[**ROB this section does not flow smoothly, needs a second pass]

@@

\scipion stream implementation is based on periodic updates of the protocol input and output data during the image processing. 
Each protocol run in Scipion is an independent process that can additionally create more processing threads. Each run that works in streaming mode has one of it threads monitoring input and updating output, that could overlap with the computing. The separation between the execution engine and the processing logic of each algorithm marks an important difference between running a script or using \scipion.The latter is a more general and extensible approach that allows users to modify the workflow on the fly without modifying a single code line. Moreover, it also allows to quickly extend the current functionality with new methods.

%** JMRT: The following line is a more specify explanation, while the previous paragraph was more general
%The modification will not interfere with the already executed steps and may take advantage from all already computed data. By default \scipion will automatically stop after 24 hours with no microscope activity, but you may  continue the acquisition after a stop by pressing the continue button, there is no need to restart from the beginning.

@@

Since \scipion original publication we have developed many \emph{metaprotocols}, that is, 
protocols that either check the progress of other protocols or compare the results of equivalent protocols.

### 2018-03-19 3.workflow_scilifelab.tex

\subsubsection{Infrastructure}
[** to be done]

>>>>

\subsubsection{Infrastructure}
At the heart of the SciLifeLab computational infrastructure is a storage and pre-processing server (the
staging server). This machine has roughly 200 TB of storage (4 ZFS RAIDZ2 pools
with 11 HDDs each), 2 NVIDIA GeForce GTX 1070 GPUs, 2 Intel Xeon E5-2630v4 CPUs
(10 cores, 2.2 GHz, HT), 384 GB RAM, and a dual-port 10 GbE network card. The
storage pool is exported via NFS and Samba, so the microscope computers can
write data there directly and other machines can access it.

Unfortunately the K2 computer writes data to a local SSD RAID, the Falcon-III to
a dedicated storage server (the offload server), in order to avoid interruption
of data collection due to network issues. So when users start data collection,
they start a script that continously moves the produced data to the staging
server.

By having all data on the staging server, in an organized folder structure, we
can run pre-processing directly on the server. If processing is started soon
after data collection the incoming file data should still be in RAM and does not
have to be read from disk, which is important with performance in mind. Users
can copy their data to external USB drives from two workstations in the
microscope room, that have access to the storage pool via NFS.
There is also a dedicated download server with access to the NFS export,
reachable from the Internet. Here users can log in to a restricted shell that
allows downloads via rsync (over SSH) or SFTP.

All these computers are conntected to a 10 GbE network switch. This is a private
network without external access. The only machine accessible from the Internet
is the data download server, which has a dual-port 10 GbE network adapter (one
used for the private network, one for the external network). Both the K2
computer and the Falcon-III offload server had one unused 10GbE interface that
could be used to connect them to our private network, without having to
interfere with the default setup.
